### 2017-07-17 main.tex
Remove includegraphics from the paper (PLOS doesn't want it), and tag all figures as 300dpi.
Whoops, remove author credit assignment fully.
Minor wording change.

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{A Fast and Accurate Zebra Finch Syllable Detector}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Ben Pearre\textsuperscript{1,a,\textcurrency},
L.~Nathan Perkins\textsuperscript{1,b},
Jeffrey E.~Markowitz\textsuperscript{2,c},
Timothy J.~Gardner\textsuperscript{1,d}
\\
\bigskip
\textsuperscript{1} Department of Biology, Boston University, Boston, Massachusetts, United States of America\\
\textsuperscript{2} Department of Neurobiology, Harvard Medical School, Boston, Massachusetts, United States of America
\\
\bigskip

@@

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  \includegraphics[width=\textwidth]{Fig1}
  \caption{The spectrogram of the song of the bird ``lny64'', used as an example
    throughout this paper.  This image was made by superposing the
    spectra of our 2818 aligned songs.  Our example detection points,
    $t^*_1\ldots t^*_6$, are shown as red lines, with example recognition
    regions of 30 ms $\times$ 1--8 kHz marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Fig2}
  % 9x10 inches
  % Fonts: Helvetica, scaled 130%
  \caption{Each plot shows one network output unit's responses to all
    2818 presentations of lny64's song shown in \fig{fig:song}.  We
    show only the syllables $t^*_1$, $t^*_4$, and $t^*_6$, and we do
    not show the non-response to presentation of non-song. The
    horizontal axis is time relative to the beginning of the aligned
    song, and the vertical axis is an index for the 2818 individual
    song presentations. The grey shading shows the audio amplitude of
    song Y at time T. Detection events on training songs are shown in
    cyan, with detections of unseen test songs in red.  To provide an
    intuition of intra-song variability, songs have been stably sorted
    by the time of detection events; thus, each of the three detection
    graphs shows the songs in a different order.}
  \label{fig:detection_raster}
\end{figure}

@@

\begin{figure}
  % Width 10, height 4, font 100%
  \includegraphics[width=\textwidth]{Fig3}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{Fig4}
  \caption{Timing varies as the FFT frame interval changes.  Here we
    show results for the ideal detector and the LabVIEW and
    Swift+serial implementations, for the constructed
    $\delta$-syllable and for trigger $t^*_4$ of lny64's song.  The
    lines show latency; error bars are standard deviation (jitter).  Points have
    been shifted horizontally slightly for clarity; original positions are [0.5 1
      1.5 2 4] ms.}
  \label{fig:TimingVsFrame}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=8cm]{Fig5}
  \end{center}
  \caption{Timing data for lny64's 6 test syllables, for the ideal and the
    Swift+serial detectors, with an FFT frame rate of 1.5 ms.  Point
    centres show latency; error bars show jitter.}
  \label{fig:TimingVsSyllable}
\end{figure}

@@

We compared latency and jitter across our different detector
implementations for the $\delta$-syllable and lny64's $t^*_4$, again with
$t_\mathrm{fft}=1.5$ ms.  Results are shown in Table~\ref{table:TimingVsDetector}.
These data are also plotted in \fig{fig:TimingVsDetector}, and
\fig{fig:timing} gives a more detailed view of what the timing curves
look like for the five implementations of our detector on lny64's $t^*_4$.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=8cm]{Fig6}
  \end{center}
  \caption{The different detectors for the constructed
    $\delta$-syllable and for lny64's song at $t^*_4$.  Point centres
    show latency; error bars show jitter.}
  \label{fig:TimingVsDetector}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[width=8cm]{Fig7}
  \end{center}
  \caption{Raw timing curves for all detectors measured during
    detection of lny64's $t^*_4$ using 1.5-ms frames.  We extract the trigger events from each curve, from which we obtain the mean---latency---and
    standard deviation---jitter.}
  \label{fig:timing}
\end{figure}

>>>>

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{A Fast and Accurate Zebra Finch Syllable Detector}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Ben Pearre\textsuperscript{1,\textcurrency},
L.~Nathan Perkins\textsuperscript{1},
Jeffrey E.~Markowitz\textsuperscript{2},
Timothy J.~Gardner\textsuperscript{1}
\\
\bigskip
\textsuperscript{1} Department of Biology, Boston University, Boston, Massachusetts, United States of America\\
\textsuperscript{2} Department of Neurobiology, Harvard Medical School, Boston, Massachusetts, United States of America
\\
\bigskip

@@

\begin{figure}
  % Width: 8, Height: 3, Fonts scale: 120%
  %\includegraphics[width=\textwidth]{Fig1}
  \caption{The spectrogram of the song of the bird ``lny64'', used as an example
    throughout this paper.  This image was made by superposing the
    spectra of our 2818 aligned songs.  Our example detection points,
    $t^*_1\ldots t^*_6$, are shown as red lines, with example recognition
    regions of 30 ms $\times$ 1--8 kHz marked as rectangles.}
  \label{fig:song}
\end{figure}

@@

\begin{figure}
  %\includegraphics[width=\textwidth]{Fig2}
  % 9x10 inches
  % Fonts: Helvetica, scaled 130%
  \caption{Each plot shows one network output unit's responses to all
    2818 presentations of lny64's song shown in \fig{fig:song}.  We
    show only the syllables $t^*_1$, $t^*_4$, and $t^*_6$, and we do
    not show the non-response to presentation of non-song. The
    horizontal axis is time relative to the beginning of the aligned
    song, and the vertical axis is an index for the 2818 individual
    song presentations. The grey shading shows the audio amplitude of
    song Y at time T. Detection events on training songs are shown in
    cyan, with detections of unseen test songs in red.  To provide an
    intuition of intra-song variability, songs have been stably sorted
    by the time of detection events; thus, each of the three detection
    graphs shows the songs in a different order.}
  \label{fig:detection_raster}
\end{figure}

@@

\begin{figure}
  % Width 10, height 4, font 100%
  %\includegraphics[width=\textwidth]{Fig3}

@@

\begin{figure}
  %\includegraphics[width=\textwidth]{Fig4}
  \caption{Timing varies as the FFT frame interval changes.  Here we
    show results for the ideal detector and the LabVIEW and
    Swift+serial implementations, for the constructed
    $\delta$-syllable and for trigger $t^*_4$ of lny64's song.  The
    lines show latency; error bars are standard deviation (jitter).  Points have
    been shifted horizontally slightly for clarity; original positions are [0.5 1
      1.5 2 4] ms.}
  \label{fig:TimingVsFrame}
\end{figure}

@@

\begin{figure}
  \begin{center}
    %\includegraphics[width=8cm]{Fig5}
  \end{center}
  \caption{Timing data for lny64's 6 test syllables, for the ideal and the
    Swift+serial detectors, with an FFT frame rate of 1.5 ms.  Point
    centres show latency; error bars show jitter.}
  \label{fig:TimingVsSyllable}
\end{figure}

@@

We compared latency and jitter across our different detector
implementations for the $\delta$-syllable and lny64's $t^*_4$, again with
$t_\mathrm{fft}=1.5$ ms.  Results are shown in Table~\ref{table:TimingVsDetector} and \fig{fig:TimingVsDetector}.
\fig{fig:timing} gives a more detailed view of what the timing curves
look like for the five implementations of our detector on lny64's $t^*_4$.

@@

\begin{figure}
  \begin{center}
    %\includegraphics[width=8cm]{Fig6}
  \end{center}
  \caption{The different detectors for the constructed
    $\delta$-syllable and for lny64's song at $t^*_4$.  Point centres
    show latency; error bars show jitter.}
  \label{fig:TimingVsDetector}
\end{figure}

\begin{figure}
  \begin{center}
    %\includegraphics[width=8cm]{Fig7}
  \end{center}
  \caption{Raw timing curves for all detectors measured during
    detection of lny64's $t^*_4$ using 1.5-ms frames.  We extract the trigger events from each curve, from which we obtain the mean---latency---and
    standard deviation---jitter.}
  \label{fig:timing}
\end{figure}
